Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-10-14 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:10:14	22:33:26	(Wed14.Oct)

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This is because MVDR relies on estimating and inverting a covariance matrix. We have shown that in systems with less than $\approx$32 channels the complexity can be reduced and the implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014}. In larger systems the inversion step is the bottleneck and space reduction techniques more viable. In clinical ultrasound, where the transmit beams are focused and the spatial sparse, we obtained similar results running our GPU implementation of MVDR in beamspace~\cite{Asen2013}. Closely related techniques include assuming spatial stationarity in the narrow beam to form a Toepliz structued covariance matrix that is easier to invert~\cite{Asl2012} a space reduction technique , which is a technique to . However, even this near optimal implementation is slow compared to DAS.

>>>>

In many cases MVDR can improve the contrast and resolution of active sonar images compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, while the computational complexity of conventional beamformers are linear with the number of channels, O($M$), MVDR is at O($M^3$). This is because MVDR relies on estimating and inverting a covariance matrix. We have shown that in systems with less than $\approx$32 channels the complexity can be reduced and the implementation accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014}. In larger systems the inversion step is the bottleneck and space reduction techniques more viable. In clinical ultrasound, where the transmit beams are focused and the spatial domain is sparse, we reduced  running our GPU implementation of MVDR in beamspace~\cite{Asen2013}. Two closely related techniques to recude is to form a simpler use principal component analysis (PCA)~\cite{Kim2014}, and to assume spatial stationarity to form more easily invertible Toepliz matrices~\cite{Asl2012}. At best these methods reduce the complexity to O($M^2$).
